\roottitle{Experience}

\headedsection
{\href{https://www.appt-health.co.uk/}{Appt Health}} {\textsc{London, United Kingdom}}
{
	\headedsubsection
	{Lead Developer} {July 2020 - Present}
	{
		\bodytext{Appt Health helps the NHS provide preventative healthcare by automating the call and recall process for patients. We have automated SMS and letter invitation channels and a GUI booking tool for staff calling patients over the phone.
		
		As the lead developer at Appt Health since the project's inception, I have developed and maintained a software system that handles sensitive patient data and that integrates with several NHS APIs requiring complicated assurance processes. The clinical risk involved in healthcare requires a rigorous approach to all aspects of development and part of my job is to ensure these standards are met.
		
		I've led and managed a small team of other developers; doing so has been an exciting challenge that has further developed my technical and teamworking skills. It is my responsibility to set our software development standards, encourage and train other developers, manage our backlog and sprints, have the final say on large architectural or security decisions and evaluate new technical hires.}
		\inlineheadsection
		{Stack:} {C\# Dotnet Core, ASP.NET, Docker, SOAP \& REST APIs, ABP Framework, DDD, BDD, Razor pages, Angular, Postgres, Git}
	}
}

\headedsection
{\href{https://theday.co.uk/}{The Day News \& Media}} {\textsc{London, United Kingdom}}
{
	\headedsubsection
	{Full Stack Developer} {July 2018 -- June 2020}
	{
		\bodytext{The Day had a legacy bespoke static site generator; my work revolved around gradually replacing this system with a bespoke Rails CMS. I worked as part of a small team but was for most of the time the sole developer. I had chance to work in a test-driven development environment which was a formative experience in my technical development, and to to manage both the technical and non-technical needs of a long-term project.}
		\inlineheadsection
		{Stack:} {Ruby On Rails, Git, Docker, TDD, AWS, Svelte, Sass, Elasticsearch, Redis, Postgres}
	}
}

\headedsection
{\href{https://www.nublue.co.uk/}{Nublue}} {\textsc{Lancaster, United Kingdom}}
{
	\headedsubsection
	{PHP Developer} {Oct 2015 -- Jan 2018}
	{
		\bodytext{Nublue is a web development agency, for which I worked on a number of ecommerce sites. For example, I was the lead backend developer on a CakePHP new build; I worked very closely with the client and with the frontend devs.}
		\inlineheadsection 
		{Stack:} {PHP, Magento, CakePHP, Laravel, Git, MySQL}
	}
}

